---
title: "Data Parse"
author: "Team"
date: "February 13, 2016"
output: html_document
---
#NEED 2 functions.
Anamolyies will take 10 Complaints

```{r}
#setwd("/Users/bobminnich/Documents/Columbia/Courses/Applied_Data_Science/project2-group3/data")

#df = read.csv("311_Short Dataset.csv")
#Filter for noises
#Noise_filter = grepl("Noise",df$Complaint.Type)
#df.noise = df[Noise_filter,]
#setwd("/Users/bobminnich/Documents/Columbia/Courses/Applied_Data_Science/")
#df = read.csv("311_1 Year.csv")
#df = read.csv("311_Full_Filtered.csv")
#df = df[1:(nrow(df)/8),]

#df = readRDS("full_filtered.rds")

```

Parse Dates into columns
```{r}
date_clean <- data.frame(do.call('rbind', strsplit(as.character(df$Created.Date),"\\s+")))
date_clean$X1 = as.Date(as.character(date_clean$X1),format ="%m/%d/%Y")
colnames(date_clean) = c("Date", "Time", "AM/PM")
df = cbind(df,date_clean)


date_clean <- data.frame(do.call('rbind', strsplit(as.character(df$Created.Date),"\\s+")))
month_clean <- data.frame(do.call('rbind', strsplit(as.character(Complaints_total$Date),"-")))


```

```{r}
setwd("/Users/bobminnich/Documents/Columbia/Courses/Applied_Data_Science/")

df = readRDS("full_filtered.rds")

df$Complaint.Type[df$Complaint.Type == "HEATING"] = "HEAT/HOT WATER"

#Filter by Date

```

Filter out Complaints to find the top 10 within the past # of days
```{r}
library(dplyr)
#library(plyr)
library(ggplot2)
#percentage_min = 0.05
Top = 10
Past_days = 30
todays_date = Sys.Date()
date_filtered = filter(df,Date>(todays_date - Past_days))

grop_by.Complaint.Type <- group_by(date_filtered, Complaint.Type)
Complaint.Type <- summarize(grop_by.Complaint.Type,count = n())
Complaint.Type$percent <- Complaint.Type$count/sum(Complaint.Type$count)


Filter_Index = order(Complaint.Type$percent, decreasing = TRUE)
Complaint.Type_filtered = Complaint.Type[Filter_Index[1:Top],]
Unique_Complaints = as.character(Complaint.Type_filtered$Complaint.Type)

ggplot(Complaint.Type_filtered, aes(x = factor(Complaint.Type), y = percent))+
    geom_bar(stat="identity")+
    coord_flip()
```

#Line Plots
```{r}
df_Unique_Complaints = filter(date_filtered,as.character(date_filtered$Complaint.Type) %in%  Unique_Complaints)

grop_by.Date.Complaint <- group_by(df_Unique_Complaints, Date,Complaint.Type)
Top.Complaints.Day <- summarise(grop_by.Date.Complaint,count = n())

ggplot(data=Top.Complaints.Day, aes(x=Date, y=count, group=Complaint.Type, colour=Complaint.Type)) +
    geom_line() +
    geom_point()

```
#######################
#####################################################################
############################################################################################
#####################################################################
#######################
#######################
#####################################################################
############################################################################################
#####################################################################
#######################
#######################
#####################################################################
############################################################################################
#####################################################################
#######################

```{r}
library(AnomalyDetection)
Anomaly_Detector = function(DataFrame_Total, Top.Complaints.Day, Compliant_Input){
  DataFrame = Top.Complaints.Day
  #DataFrame = DataFrame_Total
  DataFrame_Filtered = filter(DataFrame, Complaint.Type == Compliant_Input)
  DataFrame_Filtered2 = DataFrame_Filtered[,c("Date", "count")]
  DataFrame_Filtered2$Date = as.POSIXct(DataFrame_Filtered2$Date)
  
  if(dim(DataFrame_Filtered2)[1]<50){
    return(0)
    }else{
  #Apply Detection
  res = AnomalyDetectionTs(DataFrame_Filtered2, max_anoms=0.02, direction='pos', plot=FALSE,piecewise_median_period_weeks = 2)
  print(res)
    }
  if(length(res$anoms) == 0){
    return(0)
  }else{
  #print(paste("NUMBER OF ANAMOLIES",length(res$anoms[,2])))
  #print(res$anoms[,1])
  #Find in Heat where the anomolies are:
  #anom_index = which(Top.Complaints.Day$count %in% res$anoms[,2] )
  anom_index = which(DataFrame$count %in% res$anoms[,2] )
  DataFrame_anom = DataFrame[anom_index,]
  #df_anom_index = which(DataFrame_Total$Date %in% DataFrame_anom$Date)
  a = filter(DataFrame_anom, Complaint.Type == Compliant_Input )
  return(a)
  }
}
```

```{r}
Compliant_Input ="DOF Property - Update Account"
  DataFrame = Complaints_total
  #DataFrame = DataFrame_Total
  DataFrame_Filtered = filter(DataFrame, Complaint.Type == Compliant_Input)
  DataFrame_Filtered2 = DataFrame_Filtered[,c("Date", "count")]
  DataFrame_Filtered2$Date = as.POSIXct(DataFrame_Filtered2$Date)
  
  #Apply Detection
  res = AnomalyDetectionTs(DataFrame_Filtered2, max_anoms=0.02, direction='pos', plot=FALSE,piecewise_median_period_weeks = 2)

  #print(paste("NUMBER OF ANAMOLIES",length(res$anoms[,2])))
  #print(res$anoms[,1])
  #Find in Heat where the anomolies are:
  #anom_index = which(Top.Complaints.Day$count %in% res$anoms[,2] )
  anom_index = which(DataFrame$count %in% res$anoms[,2] )
  DataFrame_anom = DataFrame[anom_index,]
  #df_anom_index = which(DataFrame_Total$Date %in% DataFrame_anom$Date)
  #a = filter(df[df_anom_index,], Complaint.Type == Compliant_Input )
  return(DataFrame_anom)

```


```{r}
library(dplyr)
All.Date.Complaint <- group_by(df, Date,Complaint.Type)
Complaints_total <- summarise(All.Date.Complaint,count = n())

anaom_df = data.frame()
UniqueComplaints = as.character(unique(df$Complaint.Type))
#UniqueComplaints = c("PAINT - PLASTER" ,"HEAT/HOT WATER" )
anaom_df = data.frame()

for(i in UniqueComplaints){
  test = Anomaly_Detector(df,Complaints_total, i)
  if(test == 0){
    
  }else{
  test_df = data.frame(test)
  anaom_df = rbind(anaom_df,test_df)
  }
}
```


 [1] "HEAT/HOT WATER"           "Street Light Condition"   "Street Condition"         "PLUMBING"                
 [5] "GENERAL CONSTRUCTION"     "Blocked Driveway"         "Water System"             "PAINT - PLASTER"         
 [9] "Illegal Parking"          "Traffic Signal Condition"

```{r}
#This process takes the original data frame and the complaints dataframe that is grouped by day and by compalint. It then looks for the complaint passed into the function, In this case Heat and Hot water, and returns the index of the anamolies according to DATE, this is why we then filter it again on the same complaint.

```

```{r}

#Need list of dates from entire dataframe that will give us counts for all the complaints. This can be used repeatedly if necessary
All.Date.Complaint <- group_by(df, Date,Complaint.Type)
Complaints_total <- summarise(All.Date.Complaint,count = n())
todays_date = Sys.Date()

Complaint = "HEAT/HOT WATER"
#Complaint = "Water System"
#Complaint = "PAINT/PLASTER"

Past_days = 30


#Use Anonaly detector to return index anomalies of specic complaints of entire original dataframe
test = Anomaly_Detector(df,Complaints_total, Complaint)
#Use index to apply to orignal dataframe
Anamolies = df[test,]
#Filter the anamolies based on the complaint used in the search
output = filter(Anamolies, Complaint.Type == Complaint)




#Create filter to just look at defined complaints for entire dataframe
complaint_filter = filter(df, Complaint.Type == Complaint)

#Group for suming 
grop_by.Date.Complaint <- group_by(complaint_filter, Date,Complaint.Type)
#Sum each complaint per date
DefComplaint.Day <- summarise(grop_by.Date.Complaint,count = n())

#Organize for Anamolies
group_anoms.Date.Complaint <- group_by(output[,c("Date", "Complaint.Type")], Date,Complaint.Type)
Sum_group_anoms <- summarise(group_anoms.Date.Complaint,count = n())


b = ggplot(data=DefComplaint.Day, aes(x=Date, y=count, group=Complaint.Type, colour=Complaint.Type)) +
    geom_line() +
    geom_point()+ 
    xlim(c(Sys.Date()-20*4, Sys.Date()))

Sum_group_anoms_dates = filter(Sum_group_anoms,Date>(todays_date - Past_days))

if(length(Sum_group_anoms_dates$count) > 0){
  MainTitle = paste("Timeline of Complaint:", Complaint)
  b +geom_point(data=Sum_group_anoms_dates, aes(x=Date, y=count, col = "blue")) +
    ggtitle(MainTitle)+ 
    theme(legend.position="none")
}else{
  MainTitle = paste("Timeline of Complaint:", Complaint, "\n No Anamolies Detected")
  b + ggtitle(MainTitle)+ 
    theme(legend.position="none")
}

```



Multiple Plot Attempts
```{r}

b = ggplot(data=DefComplaint.Day, aes(x=Date, y=count, group=Complaint.Type, colour=Complaint.Type)) +
    geom_line() +
    geom_point()#+ 
    #xlim(c(Sys.Date()-20*4, Sys.Date()))

for( i in Unique_Complaints){

  Complaint = i
  
  #Use Anonaly detector to return index anomalies of specic complaints of entire original dataframe
  test = Anomaly_Detector(df,Complaints_total, Complaint)
  #Use index to apply to orignal dataframe
  Anamolies = df[test,]
  #Filter the anamolies based on the complaint used in the search
  output = filter(Anamolies, Complaint.Type == Complaint)
  
  #Create filter to just look at defined complaints for entire dataframe
  complaint_filter = filter(df, Complaint.Type == Complaint)
  
  #Group for suming 
  grop_by.Date.Complaint <- group_by(complaint_filter, Date,Complaint.Type)
  #Sum each complaint per date
  DefComplaint.Day <- summarise(grop_by.Date.Complaint,count = n())
  
  #Organize for Anamolies
  group_anoms.Date.Complaint <- group_by(output[,c("Date", "Complaint.Type")], Date,Complaint.Type)
  Sum_group_anoms <- summarise(group_anoms.Date.Complaint,count = n())
  
  b + geom_line(data=DefComplaint.Day, aes(x=Date, y=count, group=Complaint.Type, colour=Complaint.Type)) +
    geom_point()+ 
    xlim(c(Sys.Date()-20*4, Sys.Date()))

  
  Sum_group_anoms_dates = filter(Sum_group_anoms,Date>(todays_date - Past_days))
  
  if(length(Sum_group_anoms_dates$count) > 0){
    b=b +geom_point(data=Sum_group_anoms_dates, aes(x=Date, y=count, col = "blue")) 
  }else{
    b = b
  }
}
```


HEALTH SYSTEM

Statistics
```{r}

#Could change this to filter and pass through everything
#All.Date.Complaint <- group_by(df, Date,Complaint.Type)
#Complaints_total <- summarise(All.Date.Complaint,count = n())


#Have to add months to columns
month_clean <- data.frame(do.call('rbind', strsplit(as.character(Complaints_total$Date),"-")))
colnames(month_clean) = c("Year", "Month", "Day")
Complaints_total_grid = cbind(Complaints_total, month_clean)
Complaints_total_grid$Month = as.numeric(Complaints_total_grid$Month)


#group.Month <- group_by(Complaints_total_grid[,c("Month", "Complaint.Type")], Month,Complaint.Type)
#Sum_group_Month<- summarise(group.Month,count = n())

#Create matrix to store statistics
stat_store = matrix(0, ncol = length(unique(Complaints_total_grid$Complaint.Type)), nrow = 36)
stat_store = as.data.frame(stat_store)
colnames(stat_store) = unique(Complaints_total_grid$Complaint.Type)

#Loop through all and calculate 
for(i in unique(Complaints_total_grid$Complaint.Type)){
  index = 1
  filtered = filter(Complaints_total_grid, Complaint.Type == i)
  count = 1
  for(j in c(1:12)){
    filtered_month = filter(filtered, Month == j)
    quantiles = quantile(filtered_month$count, c(.10, .50, .90))
    stat_store[c((count):(count+2)),i] = quantiles
    count = count + 3
  }
  index = index + 1

}

```


```{r}

# 
# Top = 10
# Past_days = 30
# date_filtered = filter(df,Date>(todays_date - Past_days))
# 
# grop_by.Complaint.Type <- group_by(date_filtered, Complaint.Type)
# Complaint.Type <- summarize(grop_by.Complaint.Type,count = n())
# Complaint.Type$percent <- Complaint.Type$count/sum(Complaint.Type$count)
# 

#Filter_Index = order(Complaint.Type$percent, decreasing = TRUE)
#Complaint.Type_filtered = Complaint.Type[Filter_Index[1:Top],]
#Unique_Complaints = as.character(Complaint.Type_filtered$Complaint.Type)

#Filter statistics based on complaints
top_stat_store = stat_store[,Unique_Complaints]

#Filter on month 
test = 2
start_date = "2015-02-01"
end_date = "2015-02-28"
month_fiter = filter(Complaints_total_grid[,c("Date","Month", "Complaint.Type", "count")],Month == test & Complaint.Type %in% Unique_Complaints & Date < end_date & Date >start_date )
group.Month <- group_by(month_fiter, Month,Complaint.Type)
Sum_group_Month<- summarise(group.Month,avg = mean(count))

#Filter for Jan
Jan = top_stat_store[1:3,]
Feb = top_stat_store[4:6,]
Mar = top_stat_store[7:9,]
Apr = top_stat_store[10:12,]
May = top_stat_store[13:15,]
Jun = top_stat_store[16:18,]
Jul = top_stat_store[19:21,]
Aug = top_stat_store[22:24,]
Sep = top_stat_store[25:27,]
Oct = top_stat_store[28:30,]
Nov = top_stat_store[31:33,]
Dec = top_stat_store[34:36,]

#Create color matrix for heat map
Jan = Feb
Jan_color = Feb[1,]
colnames(Jan_color)

for( i in Sum_group_Month$Complaint.Type){
  month_fiter2 = filter(Sum_group_Month,Complaint.Type == i)
  if(month_fiter2$avg<Jan[,i][1]){
    Jan_color[1,i] = 1
  }else if(month_fiter2$avg<Jan[,i][2]){
    Jan_color[1,i] = 2
  }else if(month_fiter2$avg<Jan[,i][3]){
    Jan_color[1,i] = 3
  }else{
    Jan_color[1,i] = 4
  }
}
    


```


```{r}
a = data.frame(t(Jan_color))
a$names = rownames(a)
a$Health = 1
colnames(a) = c("X1", "names", "Health")
rownames(a) = c(1:nrow(a))
ggplot(a, aes(Health, names, width=.01)) + 
  geom_tile(aes(fill = X1), colour = "white")  +
  scale_fill_gradient(low = "LightSkyBlue", high = "LightCoral", na.value = "black", limits=c(1, 4))+ 
  theme(axis.ticks = element_line(size = 0), axis.text.x = element_text(size = 0)) + 
  xlab("Heath of System") +
  theme(panel.background = element_blank())


```






Statistics
```{r}
test = function(crazyf, month, Unique_Complaints){
#Have to add months to columns
month_clean <- data.frame(do.call('rbind', strsplit(as.character(crazyf$Date),"-")))
colnames(month_clean) = c("Year", "Month", "Day")
Complaints_total_grid = cbind(crazyf, month_clean)
Complaints_total_grid$Month = as.numeric(Complaints_total_grid$Month)


group.Month <- group_by(Complaints_total_grid[,c("Month", "Complaint.Type")], Month,Complaint.Type)
Sum_group_Month<- summarise(group.Month,count = n())

#Create matrix to store statistics
stat_store = matrix(0, ncol = length(unique(Complaints_total_grid$Complaint.Type)), nrow = 36)
stat_store = as.data.frame(stat_store)
colnames(stat_store) = unique(Complaints_total_grid$Complaint.Type)

#Loop through all and calculate 
for(i in Unique_Complaints){
  index = 1
  filtered = filter(Complaints_total_grid, Complaint.Type == i)
  count = 1
  for(j in c(1:12)){
    filtered_month = filter(filtered, Month == j)
    quantiles = quantile(filtered_month$count, c(.10, .50, .90))
    stat_store[c((count):(count+2)),i] = quantiles
    count = count + 3
  }
  index = index + 1

}

top_stat_store = stat_store[,Unique_Complaints]

#Filter on month 
test = month
start_date = "2015-02-01"

end_date = "2015-02-28"
month_fiter = filter(Complaints_total_grid[,c("Date","Month", "Complaint.Type", "count")],Month == test & Complaint.Type %in% Unique_Complaints & Date < end_date & Date >start_date )
group.Month <- group_by(month_fiter, Month,Complaint.Type)
Sum_group_Month<- summarise(group.Month,avg = mean(count))

#Filter for Jan
Jan = top_stat_store[1:3,]
Feb = top_stat_store[4:6,]
Mar = top_stat_store[7:9,]
Apr = top_stat_store[10:12,]
May = top_stat_store[13:15,]
Jun = top_stat_store[16:18,]
Jul = top_stat_store[19:21,]
Aug = top_stat_store[22:24,]
Sep = top_stat_store[25:27,]
Oct = top_stat_store[28:30,]
Nov = top_stat_store[31:33,]
Dec = top_stat_store[34:36,]

if( month == 1){
    Calc = Jan
}else if( month == 2){
    Calc = Feb
}else if( month == 3){
    Calc = Mar

}else if( month == 4){
    Calc = Apr

}else if( month == 5){
    Calc = May

}else if( month == 6){
  Calc = Jun
  
}else if( month == 7){
  Calc = Jul
  
}else if( month == 8){
  Calc = Aug
  
}else if( month == 9){
  Calc = Sep
  
}else if( month == 10){
  Calc = Oct
  
}else if( month == 11){
  Calc = Nov
  
}else {
  Calc = Dec
}

#Create color matrix for heat map
Jan_color = Feb[1,]
colnames(Jan_color)

for( i in Sum_group_Month$Complaint.Type){
  month_fiter2 = filter(Sum_group_Month,Complaint.Type == i)
  if(month_fiter2$avg<Calc[,i][1]){
    Jan_color[1,i] = 1
  }else if(month_fiter2$avg<Calc[,i][2]){
    Jan_color[1,i] = 2
  }else if(month_fiter2$avg<Calc[,i][3]){
    Jan_color[1,i] = 3
  }else{
    Jan_color[1,i] = 4
  }
}
    
a = data.frame(t(Jan_color))
a$Complaints = rownames(a)
a$Health = 1
colnames(a) = c("Health", "Complaints", "Health")
rownames(a) = c(1:nrow(a))
return (a)
}

```

```{r}
All.Date.Complaint <- group_by(df, Date,Complaint.Type)
Complaints_total <- summarise(All.Date.Complaint,count = n())
a = test(Complaints_total, 2)

burrrr = as.character(unique(df$Borough))
b = data.frame()
for(i in burrrr){
  input = filter(df, Borough == i)
  All.Date.Complaint <- group_by(input, Date,Complaint.Type)
  Complaints_total <- summarise(All.Date.Complaint,count = n())
  a = test(Complaints_total, 2,Unique_Complaints)
  a$Borough = i
  b = rbind(b,a)
}

```

```{r}
ggplot(b, aes(Borough, Complaints)) + 
  geom_tile(aes(fill = Health), colour = "white")  +
  scale_fill_gradient(low = "LightSkyBlue", high = "LightCoral", na.value = "grey", limits=c(1, 4))
  #theme(axis.ticks = element_line(size = 0), axis.text.x = element_text(size = 0)) + 

```



```{r}
anaom_df = readRDS("Anamolies.RDS")

complaint_list = c("PAINT - PLASTER" ,"HEAT/HOT WATER" ,"Blocked Driveway")
end_date = as.Date("2014-02-26")
start_date = end_date-40*4
anaom_plotter = function(complaint_list,start_date, end_date, anaom_df){

    df_filter <- filter(df, Complaint.Type %in% complaint_list)
    grop_by.Date.Complaint <- group_by(df_filter, Date,Complaint.Type)
    Top.Complaints.Day <- summarise(grop_by.Date.Complaint,count = n())
    
    Sum_group_anoms_dates = filter(anaom_df, Complaint.Type %in% complaint_list)
    b = ggplot(data=Top.Complaints.Day, aes(x=Date, y=count, group=Complaint.Type, colour=Complaint.Type)) +
        geom_line() +
        geom_point(data=Sum_group_anoms_dates, aes(x=Date, y=count,colour = Complaint.Type), size=2)+
        xlim(c(start_date, end_date))
        
    print(b)
}

anaom_plotter(Unique_Complaints,start_date, end_date, anaom_df)

```
